Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-30 edubots_surveys.Rnw
As long as we're adding FAQ agents
I guess we could as well add the local Elvira #6

On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress. For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatobt developed on the Telegram messaging platform. In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram could operate on all devices and operating systems. The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge. Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard \cite{fernoagua2018intelligent}. This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.

>>>>

On the other hand, teaching-oriented chatbots are more sophisticated as they set personalised learning outcomes and monitor learning progress. For instance, \cite{fernoagua2018intelligent} reported on ‘eduAssistant’ a virtual teaching assistant chatbot developed on the Telegram messaging platform. In this study, the Telegram platform was chosen because it is easy to use, students are familiar with its features and it enables students to exchange messages in different formats (text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram could operate on all devices and operating systems. The ‘eduAssistant’ chatbot acts as an automatic agent between the teacher-content-student, facilitating real-time feedback loops and providing a personalised learning experience relevant to students’ skills and knowledge. Using this chatbot, educators can create interactive instances in their lectures where they pose questions to their students and the chatbot assists students who need further help by giving those more hints and reporting to their educator’s dashboard \cite{fernoagua2018intelligent}. This can help educators locate those students that need their attention and send them more educational resources relevant to their academic attainment.
